ABC - HTW Fits

### 2023-12-31 Model/abc_fit.qmd
abc group plots

---
title: ABC - HTW Fits
date: last-modified
categories: [Modeling, ALM, R, Bayesian]
image: ../images/abc_varied.png
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: true
---

@@

>>>>

---
title: ABC - HTW Fits
date: last-modified
categories: [Modeling, ALM, R, Bayesian]
image: ../images/abc_varied.png
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: false
---

@@

```{r}
#| eval: false

# Define function to process dataset
process_dataset <- function(name, dataset) {
  sample_size <- str_extract(name, "\\d+p?\\d*?M")
  posterior_cutoff <- str_extract(name, "p\\d+$")

  teter_combined <- map_dfr(dataset, "teter_results", .id = "run_name")
  te_combined <- map_dfr(dataset, "te_results", .id = "run_name")
  tr_combined <- map_dfr(dataset, "tr_results", .id = "run_name")

  plot_title_suffix <- sprintf("%s - %s", sample_size, posterior_cutoff)

  return(list(teter_combined = teter_combined,
              te_combined = te_combined,
              tr_combined = tr_combined,
              plot_title_suffix = plot_title_suffix))
}

create_density_plots <- function(processed_data) {
  teter_combined <- processed_data$teter_combined
  te_combined <- processed_data$te_combined
  tr_combined <- processed_data$tr_combined
  plot_title_suffix <- processed_data$plot_title_suffix

  # Base plot for density
  base_plot <- function(data, x_var, title, show_legend = FALSE) {
    ggplot(data, aes_string(x=x_var, color="Model")) +
      geom_density() +
      facet_wrap(~Group, scales = "free") +
      ggtitle(title) +
      theme(legend.position=ifelse(show_legend, "top", "none"))  # Toggle legend display
  }

  # Create plots, but only show legend on the first plot
  plot1 <- base_plot(teter_combined, "c", sprintf("c posterior - Test & Train - %s", plot_title_suffix),TRUE )
  plot2 <- base_plot(teter_combined, "lr", sprintf("lr posterior - Test & Train - %s", plot_title_suffix))
  plot3 <- base_plot(te_combined, "c", sprintf("c posterior - Test Only - %s", plot_title_suffix))
  plot4 <- base_plot(te_combined, "lr", sprintf("lr posterior - Test Only - %s", plot_title_suffix))
  plot5 <- base_plot(tr_combined, "c", sprintf("c posterior - Train Only - %s", plot_title_suffix))
  plot6 <- base_plot(tr_combined, "lr", sprintf("lr posterior - Train Only - %s", plot_title_suffix))

  # Combine plots and place the one with the legend (plot1) at the end so that the legend is not cut off
  density_combined <- plot1 + plot2 + plot3 + plot4 + plot5 + plot6 + 
    plot_layout(ncol = 2) 
  return(density_combined)
}

create_distance_plots <- function(processed_data) {
  teter_combined <- processed_data$teter_combined
  te_combined <- processed_data$te_combined
  tr_combined <- processed_data$tr_combined
  plot_title_suffix <- processed_data$plot_title_suffix

  # Base plot for distance
  base_dist_plot <- function(data, title, show_legend = FALSE) {
    ggplot(data, aes(x=Group, y=distance, fill=Model)) +
      stat_summary(fun=mean, geom="bar", position=position_dodge(width = 0.8)) +
      stat_summary(fun.data=mean_se, geom="errorbar", position=position_dodge(width = 0.8), width=0.25) +
      ggtitle(title) +
      theme(legend.position=ifelse(show_legend, "top", "none")) # Control the display of the legend
  }

  # Create distance plots
  dist_plot1 <- base_dist_plot(teter_combined, sprintf("Test & Train - %s", plot_title_suffix),TRUE)
  dist_plot2 <- base_dist_plot(te_combined, sprintf("Test Only - %s", plot_title_suffix),)
  dist_plot3 <- base_dist_plot(tr_combined, sprintf("Train Only - %s", plot_title_suffix))

  # Combine plots and place the one with the legend (dist_plot1) at the end
  distance_combined <- dist_plot1 + dist_plot2 + dist_plot3 + 
    plot_layout(ncol = 2) 
  return(distance_combined)
}

# Define function to save plots
save_plots <- function(density_plot, distance_plot, name) {
  sample_size <- str_extract(name, "\\d+p?\\d*?M")
  posterior_cutoff <- str_extract(name, "p\\d+$")

  density_filename <- paste0("assets/tmp_plots/density_plots_combo_abc_", sample_size, "_rmse_", posterior_cutoff, ".png")
  distance_filename <- paste0("assets/tmp_plots/distance_plots_combo_abc_", sample_size, "_rmse_", posterior_cutoff, ".png")

  ggsave(filename = here::here(density_filename), plot = density_plot, width = 10, height = 6)
  ggsave(filename = here::here(distance_filename), plot = distance_plot, width = 10, height = 6)
}

# Process datasets
processed_datasets <- lapply(names(datasets), function(name) process_dataset(name, datasets[[name]]))

# Create density plots
density_plots <- invisible(lapply(processed_datasets, create_density_plots))

# Create distance plots
distance_plots <- lapply(processed_datasets, create_distance_plots)

density_plots
distance_plots

# Save plots
invisible(lapply(seq_along(names(datasets)), function(i) save_plots(density_plots[[i]], distance_plots[[i]], names(datasets)[i])))

### OLDER

### 2023-12-31 Model/dev/scratch.qmd
abc group plots

---
title: ABC - HTW Fits
date: last-modified
categories: [Modeling, ALM, R, Bayesian]
image: ../images/abc_varied.png
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: false
---

```{r}
pacman::p_load(tidyverse,data.table,abc,future,furrr,here,patchwork, conflicted)
conflict_prefer_all("dplyr", quiet = TRUE)
walk(c("fun_alm","fun_model", "Display_Functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
ds <- readRDS(here::here("data/e1_md_11-06-23.rds"))  |> as.data.table()
dsv <- ds |> filter(condit=="Varied")  
dsc <- ds |> filter(condit=="Constant")

tMax=84
avg_dsv <- ds |> filter(condit=="Varied",expMode2=="Train") |> group_by(tr) %>%
  mutate(bandInt2 = sample(rep(c(800, 1000, 1200), each = tMax / 3), tMax, replace = FALSE)[tr]) %>%
  filter(bandInt2 == x) |> select(-bandInt2) |> group_by(tr,condit,x,expMode2) |> summarise(y=mean(y),.groups="keep") |>
  rbind(dsv |> filter(expMode2=="Test") |> group_by(condit,x,expMode2) |> summarise(y=mean(y),tr=1,.groups="keep") ) |> setDT()

avg_dsc <- ds |> filter(condit=="Constant",expMode2=="Train",tr<=tMax) |> group_by(tr, condit,x,expMode2) |> 
  summarise(y=mean(y),.groups="keep") |> rbind(dsc |> filter(expMode2=="Test") |> group_by(condit,x,expMode2) |> summarise(y=mean(y),tr=1,.groups="keep") ) |> setDT()

input_layer =  c(100,350,600,800,1000,1200)
output_layer = input_layer

```{r}
#| eval: false

@@

  density_filename <- paste0("assets/tmp_plots/density_plots_combo_abc_", sample_size, "_rmse_", posterior_cutoff, ".png")
  distance_filename <- paste0("assets/tmp_plots/distance_plots_combo_abc_", sample_size, "_rmse_", posterior_cutoff, ".png")

@@

@@

### OLDER

generate_prior_c_lr <- function(n) {
  prior_samples <- tibble(
    c = runif(n, 0.000001, 7),
    lr = runif(n, 0.000001, 7),
  )
  return(prior_samples)
}

full_sim_exam <- function(data, c, lr,pred_fun=exam.response, input_layer, output_layer,return_dat="test_data",mode="sim") {
  train_data <- data[expMode2=="Train", c("condit","tr","expMode2", "x","y")] 
  test_data <- data[expMode2=="Test", c("condit","tr","expMode2", "x","y")] 
  trainVec=sort(unique(train_data$x))
 if (train_data$condit[1] != "Varied") {
  trainVec <- c(0, trainVec)
}

  train_results <- alm.sim(train_data, c, lr, input_layer, output_layer)

  test_prediction <- map_dbl(test_data$x, ~ pred_fun(.x, c, input_layer, 
                                                     output_layer, train_results$wm,  trainVec=trainVec))

  train_data$pred <- train_results$d$almResp
  test_data$pred <- test_prediction

  #fd <- rbind(train_data,test_data)
  fd = eval(parse(text=paste0("rbind(",return_dat,")")))
  if(mode=="sim"){return(fd$pred)
    }else {return(fd)}

}

full_sim_alm <- function(data, c, lr,pred_fun=alm.responseOnly, input_layer, output_layer,return_dat="test_data",mode="sim") {
  train_data <- data[expMode2=="Train", c("condit","tr","expMode2", "x","y")] 
  test_data <- data[expMode2=="Test", c("condit","tr","expMode2", "x","y")] 
  trainVec=sort(unique(train_data$x))

  train_results <- alm.sim(train_data, c, lr, input_layer, output_layer)
  test_prediction <- map_dbl(test_data$x, ~ alm.responseOnly(.x, c, input_layer, output_layer, train_results$wm,  trainVec=trainVec))

  train_data$pred <- train_results$d$almResp
  test_data$pred <- test_prediction

  #fd <- rbind(train_data,test_data)
  fd = eval(parse(text=paste0("rbind(",return_dat,")")))
  if(mode=="sim"){return(fd$pred)
    }else {return(fd)}

}

full_sim_alt_exam <- function(data, c, lr, pred_fun=alt_exam, input_layer, output_layer,return_dat="test_data",mode="sim") {
  train_data <- data[expMode2=="Train", c("condit","tr","expMode2", "x","y")] 
  test_data <- data[expMode2=="Test", c("condit","tr","expMode2", "x","y")] 
  trainVec=sort(unique(train_data$x))
  trainVecY=train_data$y

  train_results <- alm.sim(train_data, c, lr, input_layer, output_layer)
  test_prediction <- map_dbl(test_data$x, ~ alt_exam(.x, c, input_layer, output_layer, train_results$wm,  trainVecX=trainVec, trainVecY=trainVecY))

  train_data$pred <- train_results$d$almResp
  test_data$pred <- test_prediction

  #fd <- rbind(train_data,test_data)
  fd = eval(parse(text=paste0("rbind(",return_dat,")")))
  if(mode=="sim"){return(fd$pred)
    }else {return(fd)}

}

abc_loss_plot <- function(abc_result,prior_samples)
{
  pgrid <- cbind(prior_samples,dist=abc_result$dist) |> mutate(dist=sqrt(dist))
  upper_limit <- quantile(pgrid$dist, 0.95)  # 95th percentile
  pgrid <- pgrid |> filter(dist <= upper_limit)
  gg_prior <- ggplot(pgrid, aes(x = c, y = lr, color = dist)) +
  geom_point() + 
  #scale_color_viridis(limits = c(NA, upper_limit)) +
  scale_color_gradient(low = "blue", high = "red",limits = c(NA, upper_limit)) +  
  geom_contour(aes(x = c, y = lr, z = dist), color = 'white') +
  labs(title = "Point Plot of pgrid", x = "c", y = "lr") +
  theme_minimal()+ ggtitle("Prior Loss")

  post_grid <- cbind(prior_samples[abc_result$region,],dist=abc_result$dist[abc_result$region],k=abc_result$unadj.values)
  gg_post <- ggplot(post_grid, aes(x = c, y = lr, color = dist)) +
  geom_point() + 
  scale_color_gradient(low = "blue", high = "red",limits = c(NA, upper_limit)) +  
  geom_contour(aes(x = c, y = lr, z = dist), color = 'white') +
  labs(title = "Point Plot of pgrid", x = "c", y = "lr") +
  theme_minimal() + ggtitle("Posterior Loss")
  gg_prior+gg_post

}

# Define the function
abc_plot <- function(abc_result, data) {

  pgrid <- cbind(prior_samples,dist=abc_result$dist) |> mutate(dist=sqrt(dist))

  # Extracting posterior samples
  posterior_samples <- abc_result$unadj.values
  colnames(posterior_samples) <- c("c", "lr")
  posterior_samples_long <- tidyr::pivot_longer(as.data.frame(posterior_samples), everything())

  # Generate posterior density plots
  postV <- ggplot(posterior_samples_long, aes(x=value)) +
    geom_density() +
    facet_wrap(~name, scales="free") +
    theme_minimal() +
    labs(x="Value", y="Density", title="Posterior Density Plots")

  # Compute summary statistics
  sum_stats <- data.frame(
    mean = apply(posterior_samples, 2, mean),
    median = apply(posterior_samples, 2, median),
    mode = apply(posterior_samples, 2, Mode) # Ensure the 'Mode' function is defined
  )
  sum_stats <- tibble::rownames_to_column(sum_stats, var="parameter")
  print(sum_stats)

  # Calculate mode for parameters c and lr
  density_c <- density(posterior_samples[, "c"])
  mode_c <- density_c$x[which.max(density_c$y)]
  density_lr <- density(posterior_samples[, "lr"])
  mode_lr <- density_lr$x[which.max(density_lr$y)]

  print(paste0("Mode of c: ", mode_c, ", Mode of lr: ", mode_lr))

  # Run simulation with full_sim_exam function
  fsv <- full_sim_exam(as.data.table(data), c=mode_c, lr=mode_lr, exam.response, input_layer, output_layer, mode="ret")

  # Generate plot for simulation results
  plot_fsv <- fsv |> 
    tidyr::pivot_longer(y:pred, names_to="Resp", values_to="vx") |> 
    ggplot(aes(x, vx, fill=Resp, group=Resp)) +
    stat_summary(geom="bar", fun="mean", position=position_dodge()) +
    scale_fill_manual(values=col_themes$wes2) +
    scale_x_continuous(breaks=sort(unique(data$x)), labels=sort(unique(fsv$x))) +
    theme(legend.title = element_blank(), legend.position="top") +
    ggtitle("Fit to Test Only")

  postV + plot_fsv
}

n_prior_samples <- 5000
prior_samples <- generate_prior_c_lr(n_prior_samples)

# 
# data=avg_dsc
# return_dat="train_data,test_data"
# return_dat="train_data"
# 
# eval(parse(text=paste0("rbind(",return_dat,")")))
# 
# paste0(rbind(parse(text=return_dat)))
#

# General function for ABC fits with model flexibility
run_abc_fits <- function(data, input_layer, output_layer, simulation_function, n_prior_samples = 1000, tol = 0.01, return_dat = "train_data,test_data") {

  input_layer =  c(100,350,600,800,1000,1200)
  output_layer = input_layer

  # Generate prior samples
  prior_samples <- generate_prior_c_lr(n_prior_samples)

    # Convert the string to a function
  if (is.character(simulation_function)) {
    simulation_function <- get(simulation_function, mode = "function")
  } else {
    simulation_function <- match.fun(simulation_function)
  }

  plan(multisession)
  # Run simulations for each prior sample
  simulation_results <- future_map_dfc(seq_len(nrow(prior_samples)), function(idx) {
    params <- prior_samples[idx, ]
    simulation_function(data=as.data.table(data), c=params$c, lr=params$lr, input_layer=input_layer, output_layer=output_layer, return_dat = return_dat)
  }, .options = furrr_options(seed = TRUE))

  # Extract target data
  target_data_train_test <- data[expMode2 %in% c("Test", "Train"), ]$y
  target_data_test <- data[expMode2 == "Test", ]$y
  target_data_train <- data[expMode2 == "Train", ]$y

  # ABC for train and test data
  abc_train_test <- abc(
    target = target_data_train_test,
    param = prior_samples,
    sumstat = do.call(rbind, simulation_results),
    tol = tol,
    method = "rejection"
  )

  # ABC for test data only
  abc_test <- abc(
    target = target_data_test,
    param = prior_samples,
    sumstat = do.call(rbind, simulation_results[85:90, ]),
    tol = tol,
    method = "rejection"
  )

    # ABC for test data only
  abc_train <- abc(
    target = target_data_train,
    param = prior_samples,
    sumstat = do.call(rbind, simulation_results[1:84, ]),
    tol = tol,
    method = "rejection"
  )

  # Return results
  tibble::lst(abc_train_test = abc_train_test, abc_test = abc_test, abc_train,data=data,n_prior_samples,prior_samples,tol, simulation_function, targets=tibble::lst(target_data_train_test, target_data_test))
}

# Example usage for different models
n_priors=200
abc_results_varied_exam <- run_abc_fits(avg_dsv, input_layer, output_layer, full_sim_exam, n_prior_samples = n_priors)
abc_results_varied_alt_exam <- run_abc_fits(avg_dsv, input_layer, output_layer, full_sim_alt_exam, n_prior_samples = n_priors)
abc_results_varied_alm <- run_abc_fits(avg_dsv, input_layer, output_layer, full_sim_alm, n_prior_samples = n_priors)

abc_results_constant_alm <- run_abc_fits(avg_dsc, input_layer, output_layer, full_sim_alm, n_prior_samples = n_priors)
abc_results_constant_exam <- run_abc_fits(avg_dsc, input_layer, output_layer, full_sim_exam, n_prior_samples = n_priors)
abc_results_constant_alt_exam <- run_abc_fits(avg_dsc, input_layer, output_layer, full_sim_alt_exam, n_prior_samples = n_priors)

# store all models in list and save to data/model_cache
model_cache <- list(
  abc_results_varied_exam = abc_results_varied_exam,
  abc_results_varied_alt_exam = abc_results_varied_alt_exam,
  abc_results_varied_alm = abc_results_varied_alm,
  abc_results_constant_alm = abc_results_constant_alm,
  abc_results_constant_exam = abc_results_constant_exam,
  abc_results_constant_alt_exam = abc_results_constant_alt_exam
)

saveRDS(model_cache,here::here(paste0("data/model_cache/abc_group_200k_",format(Sys.time(), "%H_%M_%OS"),".rds")))

n_priors=20000
args_list <- tibble::lst(
  abc_v_exam=list(data = avg_dsv, input_layer = input_layer, output_layer = output_layer, simulation_function = full_sim_exam, n_prior_samples = n_priors),
  abc_v_alt_exam=list(data = avg_dsv, input_layer = input_layer, output_layer = output_layer, simulation_function = full_sim_alt_exam, n_prior_samples = n_priors),
  abc_v_alm=list(data = avg_dsv, input_layer = input_layer, output_layer = output_layer, simulation_function = full_sim_alm, n_prior_samples = n_priors),
  abc_c_alm=list(data = avg_dsc, input_layer = input_layer, output_layer = output_layer, simulation_function = full_sim_alm, n_prior_samples = n_priors),
  abc_c_exam=list(data = avg_dsc, input_layer = input_layer, output_layer = output_layer, simulation_function = full_sim_exam, n_prior_samples = n_priors),
  abc_c_alt_exam=list(data = avg_dsc, input_layer = input_layer, output_layer = output_layer, simulation_function = full_sim_alt_exam, n_prior_samples = n_priors)
)

results <- future_map(args_list, ~do.call(run_abc_fits, .x))
saveRDS(results,here::here(paste0("data/model_cache/abc_group12_",format(Sys.time(), "%H_%M_%OS"),".rds")))

## Varied Average Fits
```{r}

k=full_sim_exam(avg_dsv, .5, .2,exam.response,input_layer, output_layer,return_dat = "train_data,test_data")

n_prior_samples <- 5000
prior_samples <- generate_prior_c_lr(n_prior_samples)

plan(multisession)
sd_v_tetr <- future_map_dfc(seq_len(nrow(prior_samples)), function(idx) {
  params <- prior_samples[idx, ]
  full_sim_exam(as.data.table(avg_dsv), params$c, params$lr,exam.response, input_layer, output_layer,return_dat = "train_data,test_data")
},.options = furrr_options(seed = T))

dst_v_tetr <- avg_dsv[expMode2=="Test" | expMode2=="Train",]$y
abc_v_tetr <- abc(
  target = dst_v_tetr,
  param = prior_samples,
  sumstat =do.call(rbind, sd_v_tetr),
  tol = .01,
  method = "rejection",
  names=colnames(dst_v_tetr)
)

dst_v_te <- avg_dsv[expMode2=="Test",]$y
sd_v_te <- sd_v_tetr[85:90,]
abc_v_te <- abc(
  target = dst_v_te,
  param = prior_samples,
  sumstat =do.call(rbind, sd_v_te),
  tol = .01,
  method = "rejection",
  names=colnames(dst_v_te)
)

abc_plot(abc_v_tetr, avg_dsv) / { abc_loss_plot(abc_v_tetr,prior_samples) }
abc_plot(abc_v_te, avg_dsv) / { abc_loss_plot(abc_v_te,prior_samples) }

## Constant Average Fits
```{r}

n_prior_samples <- 5000
prior_samples <- generate_prior_c_lr(n_prior_samples)

plan(multisession)

sd_c_tetr <- future_map_dfc(seq_len(nrow(prior_samples)), function(idx) {
  params <- prior_samples[idx, ]
  full_sim_exam(as.data.table(avg_dsc), params$c, params$lr,exam.response, input_layer, output_layer,return_dat = "train_data,test_data")
},.options = furrr_options(seed = T))

dst_c_tetr <- avg_dsc[expMode2=="Test" | expMode2=="Train",]$y

abc_c_tetr<- abc(
  target = dst_c_tetr,
  param = prior_samples,
  sumstat =do.call(rbind, sd_c_tetr),
  tol = .01,
  method = "rejection",
  names=colnames(dst_c_tetr)
)

abc_plot(abc_c_tetr, avg_dsc)

dst_c_te <- avg_dsc[expMode2=="Test",]$y
sd_c_te <- sd_c_tetr[85:90,]

abc_c_te <- abc(
  target = dst_c_te,
  param = prior_samples,
  sumstat =do.call(rbind, sd_c_te),
  tol = .01,
  method = "rejection",
  names=colnames(dst_c_te)
)

abc_plot(abc_c_tetr, avg_dsc) / { abc_loss_plot(abc_c_tetr,prior_samples) }
abc_plot(abc_c_te, avg_dsc) / { abc_loss_plot(abc_c_te,prior_samples) }

lin <- abc(target=dst_obs, param=prior_samples, sumstat=do.call(rbind, simulated_data), tol=.08, hcorr =FALSE, method = "loclinear")

posterior_samples <- lin$unadj.values
colnames(posterior_samples) <- c("c", "lr")
head(posterior_samples)
posterior_samples_long <- tidyr::pivot_longer(as.data.frame(posterior_samples), everything())

postV <- ggplot(posterior_samples_long, aes(x=value)) +
  geom_density() + facet_wrap(~name, scales="free") +
  labs(x="Value", y="Density", title="Posterior Density Plots")
postV

sum_stats <- data.frame(mean = apply(posterior_samples, 2, mean),
  median = apply(posterior_samples, 2, median), mode=apply(posterior_samples, 2, Mode))
( sum_stats=rownames_to_column(sum_stats,var="parameter") )

summary(lin)

plot(lin,prior_samples,subsample=100)
hist(lin)

cv.lin <- cv4abc(param=prior_samples, sumstat=do.call(rbind, simulated_data),nval=15,tols=c(.01,.05,.1,.2,.3,.5), method="rejection", statistic="mode")
summary(cv.lin)

cv.lin2 <- cv4abc(param=prior_samples, sumstat=do.call(rbind, simulated_data),nval=15,tols=c(.01,.05,.1,.2,.3,.5),abc.out=abc_result, method="rejection", statistic="mode")

summary(cv.lin2)

nn <- abc(target=dst_obs, param=prior_samples, sumstat=do.call(rbind, simulated_data), tol=.01, hcorr =FALSE, method = "neuralnet")

postV <- ggplot(posterior_samples_long, aes(x=value)) +
  geom_density() +
  facet_wrap(~name, scales="free") +
  theme_minimal() +
  labs(x="Value", y="Density", title="Posterior Density Plots")
postV

sum_stats <- data.frame(mean = apply(posterior_samples, 2, mean),
  median = apply(posterior_samples, 2, median), mode=apply(posterior_samples,2,Mode))
( sum_stats=rownames_to_column(sum_stats,var="parameter") )

id1 <- ds |> filter(id==3)
n_prior_samples <- 500
prior_samples <- generate_prior_c_lr(n_prior_samples)

plan(multisession)
simulated_data <- future_map_dfc(seq_len(nrow(prior_samples)), function(idx) {
  params <- prior_samples[idx, ]
  full_sim_alt_exam(as.data.table(id1), params$c, params$lr,alt_exam, input_layer, output_layer,return_dat = "train_data,test_data")
},.options = furrr_options(seed = T))

dst_obs <- id1[expMode2=="Test",]$y
dst_obs <- id1[expMode2=="Test" | expMode2=="Train",]$y

tolerance <- 0.1 * sd(dst_obs)

abc_result <- abc(
  target = dst_obs,
  param = prior_samples,
  sumstat =do.call(rbind, simulated_data),
  tol = .1,
  method = "rejection",
  names=colnames(dst_obs)
)

posterior_samples <- abc_result$unadj.values
colnames(posterior_samples) <- c("c", "lr")

posterior_samples_long <- tidyr::pivot_longer(as.data.frame(posterior_samples), everything())

postV <- ggplot(posterior_samples_long, aes(x=value)) +
  geom_density() +
  facet_wrap(~name, scales="free") +
  theme_minimal() +
  labs(x="Value", y="Density", title="Posterior Density Plots")
postV

sum_stats <- data.frame(mean = apply(posterior_samples, 2, mean),
  median = apply(posterior_samples, 2, median), mode=apply(posterior_samples,2,Mode))
( sum_stats=rownames_to_column(sum_stats,var="parameter") )

density_c <- density(posterior_samples[, "c"])
mode_c <- density_c$x[which.max(density_c$y)]
density_lr <- density(posterior_samples[, "lr"])
mode_lr <- density_lr$x[which.max(density_lr$y)]

fsv <- full_sim_alt_exam(as.data.table(id1), c=mode_c, lr=mode_lr,exam.response, input_layer, output_layer,mode="ret")

fsv |> pivot_longer(y:pred,names_to="Resp",values_to="vx") |> 
  ggplot(aes(x,vx,fill=Resp, group=Resp)) +stat_summary(geom="bar",fun="mean",position=position_dodge())+
  scale_fill_manual(values=col_themes$wes2)+
  scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(fsv$x))) +
  theme(legend.title = element_blank(), legend.position="top") +ggtitle("Fit to Test Only")

>>>>

```{r fig.width=11, fig.height=8}

# Load required libraries
pacman::p_load(tidyverse, data.table, abc, future, furrr, here, patchwork, conflicted)

@@

  density_filename <- paste0("assets/tmp_plots/density_plots_combo_abc_", sample_size, "rmse", posterior_cutoff, ".png")
  distance_filename <- paste0("assets/tmp_plots/distance_plots_combo_abc_", sample_size, "rmse", posterior_cutoff, ".png")

@@

pacman::p_load(tidyverse, data.table, abc, future, furrr, here, patchwork, conflicted)

# Function to process dataset
process_dataset <- function(name, dataset) {
  sample_size <- str_extract(name, "\\d+p?\\d*?M")
  posterior_cutoff <- str_extract(name, "p\\d+$")

  list(teter_combined, te_combined, tr_combined)
}

# Function to create and save density plots
create_density_plots <- function(data_combined, name) {
  sample_size <- str_extract(name, "\\d+p?\\d*?M")
  posterior_cutoff <- str_extract(name, "p\\d+$")
  plot_title_suffix <- sprintf("%s - %s", sample_size, posterior_cutoff)

  plot_list <- lapply(data_combined, function(data) {
    ggplot(data, aes(x = c)) + 
      geom_density(aes(color = Model)) +
      facet_wrap(~Group, scales = "free") + 
      ggtitle(sprintf("c posterior - %s - %s", data$context[1], plot_title_suffix))
  })

  density_combined <- wrap_plots(plot_list, ncol = 2)
  density_filename <- sprintf("assets/tmp_plots/density_plots_combo_abc_%srmse%s.png", sample_size, posterior_cutoff)
  ggsave(filename = here::here(density_filename), plot = density_combined, width = 10, height = 6)
}

# Function to create and save distance plots
create_distance_plots <- function(data_combined, name) {
  sample_size <- str_extract(name, "\\d+p?\\d*?M")
  posterior_cutoff <- str_extract(name, "p\\d+$")
  plot_title_suffix <- sprintf("%s - %s", sample_size, posterior_cutoff)

  dist_plot_list <- lapply(data_combined, function(data) {
    ggplot(data, aes(x = Group, y = distance, fill = Model)) +
      stat_summary(fun = mean, geom = "bar", position = position_dodge()) +
      stat_summary(fun.data = mean_se, geom = "errorbar", position = position_dodge()) +
      ggtitle(sprintf("%s - %s", data$context[1], plot_title_suffix))
  })

  distance_combined <- wrap_plots(dist_plot_list, ncol = 2)
  distance_filename <- sprintf("assets/tmp_plots/distance_plots_combo_abc_%srmse%s.png", sample_size, posterior_cutoff)
  ggsave(filename = here::here(distance_filename), plot = distance_combined, width = 10, height = 6)
}

# Load datasets
datasets <- list(
  abc_1M_p001 = readRDS(here::here("data/abc_1M_rmse_p001.rds")),
  abc_1M_p0001 = readRDS(here::here("data/abc_1M_rmse_p0001.rds")),
  abc_2M_p001 = readRDS(here::here("data/abc_2M_rmse_p001.rds")),
  abc_2M_p0001 = readRDS(here::here("data/abc_2M_rmse_p0001.rds")),
  abc_1p5M_p001 = readRDS(here::here("data/abc_1p5M_rmse_p001.rds")),
  abc_1p5M_p0001 = readRDS(here::here("data/abc_1p5M_rmse_p0001.rds"))
)

# Process and plot for each dataset
invisible(lapply(names(datasets), function(name) {
  processed_data <- process_dataset(name, datasets[[name]])
  create_density_plots(processed_data, name)
  create_distance_plots(processed_data, name)
}))

@@
